The Natural History of Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-12-05 Paper.qmd
simplified code for using public data
reducing dependencies

# To use public data, comment out dataprep.R
# and uncomment dataprepPublic.R
source("dataprep.R")
# source("dataprepPublic.R")

source("analysis.R")
source("analysis2.R") # Generates many plots. Slow!
```

@@

kable(custom.summarize(utila_df, longform_dict[1:23])) %>% kable_styling()
```

>>>>

# To use public data, comment out dataprep.R
# and uncomment load statement
source("dataprep.R")
# load("data/utilasignalingPublicData.rda")

source("analysis.R")
# source("analysis2.R") # Generates many plots. Slow!
```

@@

utila_df |> 
  dplyr::select(any_of(names(utila_df[names(longform_dict[1:23])]))) |> 
  setNames(longform_dict[1:23]) |> 
  datasummary_skim(fun_numeric = list(N = \(x) length(na.omit(x)), Range = \(x) str_glue("{min(x, na.rm=T)}-{max(x, na.rm=T)}"), Mean = Mean, SD = SD, Histogram = function(x) ""))
```
